### 2014-11-02 fundamentals/qa.tex
fixes #52

Lastly, uncertainty quantification is a process that is used on specific simulation
instantiations to statistically determine its quality. Since the cyclus 
kernel requires an input file written by the user, UQ is a process that applies 
more to those running cyclus than to those running it.  Furthermore, any UQ
results that are generated are applicable only to the scenario that is under 
analysis. Thus for cyclus UQ is well beyond the scope of core development.

>>>>

Lastly, uncertainty quantification is a process that is used on specific simulation
instantiations to statistically determine its quality. Since the \Cyclus 
kernel requires an input file written by the user, UQ is a process that applies 
to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle 
simulator, cannot make reliable statements about the uncertainty of a particular fuel 
cycle. Any UQ results are applicable only to the scenario that is under 
analysis. \Cyclus is not a panacea for due dillegence on behalf of the fuel 
cycle modeler. Thus, UQ is envisioned to be beyond the scope of core development 
and in the domain of the expert user.
